Naturalness in U(1) extensions of the MSSM

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added plots with thicker lines and larger labels to the paper, labels probably still have to be a bit bigger to be legible

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).  {\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).  {\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
